### 2017-09-21 Sections/about_the_authors.tex
Added clock sync. Added more on qkd

Peter Rohde is an ARC Future Fellow in the Centre for Quantum Software \& Information at the University of Technology Sydney (UTS:QSI), and associate member of the Hearne Institute for Theoretical Physics at Louisiana State University. He obtained a Bachelor of Computer Systems Engineering with First Class Honours, and a PhD in theoretical physics at the University of Queensland. He has worked at highly-acclaimed international institutes, including the University of Oxford, University of Queensland, Institute for Molecular Biosciences and Max-Planck Institute for the Science of Light, with over 45 publications and 1,200+ citations in quantum optics, quantum computing, quantum information theory and ecology. His theoretical proposals have inspired several leading experimental efforts, including time-bin encoded boson-sampling and sub-shot-noise limited quantum metrology. In his spare time he is a musician, composer, public speaker, charity worker, mountaineer and adrenaline junkie. He regularly speaks at prominent scientific outreach events, features in newspaper and magazine articles, and conducts radio interviews. He is a very naughty boy and was expelled from preschool.

>>>>

Peter Rohde is an ARC Future Fellow in the Centre for Quantum Software \& Information at the University of Technology Sydney (UTS:Q$|$SI$\rangle$), and associate member of the Hearne Institute for Theoretical Physics at Louisiana State University. He obtained a Bachelor of Computer Systems Engineering with First Class Honours, and a PhD in theoretical physics at the University of Queensland. He has worked at highly-acclaimed international institutes, including the University of Oxford, University of Queensland, Institute for Molecular Biosciences and Max-Planck Institute for the Science of Light, with over 45 publications and 1,200+ citations in quantum optics, quantum computing, quantum information theory and ecology. His theoretical proposals have inspired several world-leading experimental efforts, including time-bin encoded {\sc BosonSampling} and sub-shot-noise limited quantum metrology. In his spare time he is a musician, composer, public speaker, charity worker, mountaineer and adrenaline junkie. He regularly speaks at prominent scientific outreach events, features in newspaper and magazine articles, and conducts radio interviews. He is a very naughty boy and was expelled from preschool.

### 2017-09-21 Sections/cloud_quantum_computing.tex
Added clock sync. Added more on qkd

The cluster state (Sec.~\ref{sec:CSQC}), topological code (Sec.~\ref{sec:topol_codes}) and quantum random walk (Sec.~\ref{sec:QW}) models for quantum computation may find themselves to be particularly well-suited to distributed implementation, since they naturally reside on graphs, whose nodes needn't be held locally by a single user, but could instead be shared across multiple hosts with the ability for graph nodes to intercommunicate.

@@

An alternate direction, for economic reasons, is that it is unviable for a single server to host an entire computation. Rather, hosts will have limited capability, and performing large-scale computations will require employing a potentially large number of hosts cooperating and sharing resources with one another\footnote{Even some present-day massive-scale data processing and storage protocols are implemented virtually across multiple large-scale data-centres, which, for example, automatically handle geographically decentralised data redundancy and processing. Google and Amazon, for example, provide cloud services for this purpose, employed both internally, and licensed out to third parties, and the Apache Cassandra project provides an open-source equivalent. The key is for the underlying protocol to abstract this away from the user, such that they interface with the data as though it were a local asset.}. This can be regarded as the most general incarnation of distributed computation.

@@

%
% Outsourced Quantum Research
%

@@

Thus far we have focussed on computation as the key utility for outsourced quantum technologies, and certainly this is likely to be the dominant driving force behind quantum outsourcing. But of course not everyone wants to only solve complex algorithmic problems. Others may wish to study quantum systems themselves from the perspective of basic science research. Around the world, scientists are competing the set up elaborate laboratories, implementing ever increasingly complicated quantum experiments, not for the purposes of algorithmic problem solving, but for that of intellectual pursuit.

@@

The QTCP protocol presented in Sec.~\ref{sec:QTCP} provides an extensible framework for facilitating these kinds of outsourced or delegated protocols using generic quantum assets. Bear in mind that, as designed, the payload of QTCP packets could encapsulate all manner of optical states, or mediate long-distance interaction between them.

>>>>

The cluster state (Sec.~\ref{sec:CSQC}), topological code (Sec.~\ref{sec:topol_codes}) and quantum random walk (Sec.~\ref{sec:QW}) models for quantum computation may find themselves to be particularly well-suited to distributed implementation, since they naturally reside on graphs, whose nodes needn't be held locally by a single user, but could instead be shared across multiple hosts with the ability for graph nodes to intercommunicate. Then only classical communication is required to complete a computation will quantum information not localised to any particular node.

Additionally, the entangling gates which build cluster states all commute and may be implemented simultaneously in parallel. This enables a distributed cluster state to be constructed in a `patchwork' fasion, as shown in Fig.~\ref{fig:patchwork_cluster}. Now the computation is truly distributed in the sense that the computation resides collectively across the distributed cluster state, held by any number of users.

This approach overlaps with the modularised approach for quantum computation discussed in the upcoming Sec.~\ref{sec:module}, the difference being that in distributed cluster states the goal is to delocalise computations due to resource constraints, whereas for modularised computation the motivation is largely economical, driven by economy of scale.

\begin{figure}[!htb]
\includegraphics[width=0.8\columnwidth]{patchwork_cluster} 
\caption{Approach for constructing distributed cluster states across multiple nodes. The quantum channels allow neighbouring clusters in the topology to be fused together, constructing a large virtual cluster state for distributed computation. The nodes could be arbitrarily separated with optically-mediated interconnects.} \label{fig:patchwork_cluster}
\end{figure}

@@

An alternate direction, for economic reasons, is that it is unviable for a single server to host an entire computation. Rather, hosts will have limited capability, and performing large-scale computations will require employing a potentially large number of hosts cooperating and sharing resources with one another\footnote{Even some present-day massive-scale data processing and storage protocols are implemented virtually across multiple large-scale data-centres, which, for example, automatically handle geographically decentralised data redundancy and processing. Google and Amazon, for example, provide cloud services for this purpose, employed both internally, and licensed out to third parties, and the Apache Cassandra\index{Apache Cassandra project} project provides an open-source equivalent. The key is for the underlying protocol to abstract this away from the user, such that they interface with the data as though it were a local asset.}. This can be regarded as the most general incarnation of distributed computation.

@@

%
% Quantum Clock Synchronisation
%

\subsubsection{Quantum clock synchronization}\index{Quantum clock synchronisation}

\comment{Complete}

Clock synchronization is a fundamental task that is has widespread applications, ranging from navigation, telecommunications, financial transactions, the internet, and many scientific applications. Of these, the Global Positioning System (GPS) has become a day-to-day necessity for a large fraction of the human population as it has been increasingly built into smartphones and other devices. The GPS system famously relies upon very precise clock synchronization to perform its task through a process of quadrangulation from several satellites. Due to the high speed of light, one requires in practice highly synchronized clocks which are accurate to a centralized time standard to the $\sim$ns level. This allows positioning to be performed to the $\sim$m level, which is acceptable for many applications.

GPS satellites have atomic clocks that are stable to one part in $10^{13}$, so that active corrections can maintain the accurate to the $\sim$ ns level. The great success of the GPS system in turn has created a further demand for increasingly precise navigation. For example, autonomous vehicles would immediately benefit from a more precise navigation system. In principle, technology for more stable clocks is already present, with atomic clocks exceeding stabilities of those on satellites being routinely produced, and optical atomic clocks now reaching stabilities of one part in $10^{18}$ \cite{bib:ludlow2015optical}. An outstanding question is then how to synchronize these clocks given their remarkable stabilities.

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{space_3}
\caption{Quantum clock synchronization schemes. (top) The proposal by Jozsa, Dowling, and co-workers where a singlet state is shared and measured in an ensemble of qubits \cite{bib:jozsa00}. (bottom) The proposal by \cite{Lukin, Ye, and co-workers} where a GHZ state is generated between satellites to obtain measure the frequency drift at the Heisenberg limit \cite{bib:komar14}.}
\label{fig:figspace3}
\end{figure}

Several past works have examined the problem of clock synchronization in space (see also Sec. [TB: refer to other section on clock sync]). In the proposal of Jozsa and co-workers, many copies of shared entanglement in a singlet state is first distributed and stored on the clock states of an atomic clock \cite{bib:jozsa00}.  The measurement is then made by one of the parties, which collapses the states simultaneously at each party, and the time evolution of the states begins. Classical information is exchanged between them, which reveals the time elapsed since the measurement, which can be used to synchronize the clocks. While the original protocol only allowed allowed clock synchronization between two parties, similar ideas were used to extend it to a multiparty context \cite{bib:krvco2002quantum, bib:ben2011optimized, bib:ren2012clock}.

In a more recent proposal, a shared GHZ state is prepared across all the nodes of the quantum network, which allows for a quantum metrologically enhanced detection of the clock signal drift at the Heisenberg limit \cite{bib:komar14}. The use of shared resources acts to improve the overall precision, allowing for an optimal scheme for the qubit resources that are used. Several other proposals have also been made, which are quantum versions of Eddington's slow clock transport where the qubit keeps time of the transmission time \cite{bib:chuang2000quantum, bib:tavakoli2015quantum}.

Experimentally, there have been several demonstrations of the protocol, albeit at relatively short distances. Continuous time-bin entangled photons were used as the entanglement resource to obtain a time-correlation between a distance of 3 km \cite{bib:valencia2004distant}, and another technique based on Hong-Ou-Mandel interferometry was performed with a 4 km fiber link \cite{bib:quan2016demonstration}.  Several other demonstrations based on NMR \cite{bib:zhang2004nuclear, bib:kong2017implementation} have also been performed.

There are however several outstanding problems with the quantum clock synchronization scheme as presented above. In the scheme of Jozsa and co-workers, if one starts in a perfect singlet state, the scheme works as intended, but if one instead starts in the state, 
\begin{align}
\frac{1}{\sqrt{2}} \left( | 0 \rangle_A | 1 \rangle_B - e^{i \delta} | 1 \rangle_A | 0 \rangle_B \right).
\end{align}
Then one obtains an offset to the synchronizations between the two parties. In practice, such a phase could arise from decoherence induced noise, or differences in the basis conventions that the two parties choose. Thus in practice entanglement purification would to be performed to produce a singlet state with $ \\delta = 0$ before the synchronization protocol is performed.  However, it was argued that to perform the entanglement purification quantum circuit correctly, the timing of the quantum gates would need to be controlled, which requires synchronized clocks \cite{bib:preskill2000quantum} --  rendering the syncrhonization impossible. It was previously been shown that such a phase cannot be eliminated using asynchronous entanglement purification \cite{bib:yurtsever02}, and hence the protocol remains incomplete in the general case where imperfect singlet pairs are shared.

%
% Fundamental Physics Experiments
%

@@

\comment{Complete}

\subsubsection{Fundamental physics experiments}

Thus far we have focussed on computation as the key utility for outsourced quantum technologies, and certainly this is likely to be the dominant driving force behind quantum outsourcing\index{Outsourced quantum technology}. But of course not everyone wants to only solve complex algorithmic problems. Others may wish to study quantum systems themselves from the perspective of basic science research\index{Basic science research}.

@@

The availability of a globe-spanning quantum network on satellites brings the opportunity for fundamental quantum mechanical experiments and unprecedented length scales and velocities in the future. Satellite-to-satellite\index{Satellite-to-satellite} photon transfer can allow for ultra-long distance quantum communications that are not possible on Earth due to atomospheric loss. Another unique aspect of space is that satellites move at high velocities -- typically at $10^{-5} $ times the speed of light\index{Speed of light} for LEO satellites. The combination of both of these effects gives a unique opportunity for performing relativistic quantum information\index{Relativistic quantum information} experiments to test fundamental physics.

We anticipate that some of the first experiments will be extensions of what are already performed on Earth. For example, one can perform increasingly long space-based Bell violation tests\index{Bell violation} at unprecedented distances \cite{bib:yin2017satellite}. Another possibility is to examine the speed of influence of entanglement, which bound the speed of entanglement \cite{bib:yin2013lower}. In space, such experiments could be extended much further, giving tighter bounds. There are demanding technical hurdles that must be overcome to succeed at such experiments, such as the necessity for synchronized clocks (Sec.~\ref{sec:clocks}).

 In addition to examining extensions of existing experiments, the high satellite velocities can be used to perform relativistic quantum information experiments, such as entanglement tests in the presence of special\index{Special relativity} and general relativity\index{General relativity}, Wheeler's delayed choice experiment\index{Wheeler's delayed choice experiment}, and enhanced quantum metrology \cite{sec:kaltenbaek2003proof, sec:scheidl2013quantum, sec:ahmadi2014relativistic}.

The QTCP protocol presented in Sec.~\ref{sec:QTCP} provides an extensible framework for facilitating these kinds of outsourced or delegated protocols\index{Outsourced protocols}\index{Delegated protocols} using generic quantum assets. Bear in mind that, as designed, the payload of QTCP packets could encapsulate all manner of optical states, or mediate long-distance interaction between them.

### 2017-09-21 Sections/essay_security_implications_of_the_global_quantum_internet.tex
Added clock sync. Added more on qkd

With a global QKD infrastructure\index{Quantum key distribution (QKD)} in place, any person on Earth would have uncrackable encryption at their fingertips. Whilst this might be welcomed by the populace of a despotic regime (or the libertarians in a democratic one), it would clearly be unwelcome for that level of secrecy and protection to be awarded to the regime itself. Similarly, criminal and terrorist organisations would be immune to government surveillance. With widespread global adoption of QKD technology, the signals intelligence agencies of nation states would become entirely obsolete, leaving the NSA and its Five Eyes\texttrademark \,partners furious.

>>>>

With a global QKD infrastructure\index{Quantum key distribution (QKD)} in place, any person on Earth would have uncrackable encryption at their fingertips. Whilst this might be welcomed by the populace of a despotic regime (or the libertarians in a democratic one), it would clearly be unwelcome for that level of secrecy and protection to be awarded to the regime itself. Similarly, criminal and terrorist organisations would be immune to government surveillance. With widespread global adoption of QKD technology, the signals intelligence agencies of nation states would become entirely obsolete, leaving the NSA\index{National Security Agency} and its Five Eyes\texttrademark \,partners furious\index{Five Eyes}.

### 2017-09-21 Sections/introduction.tex
Added clock sync. Added more on qkd

\begin{itemize}
	\item Searching unstructured databases:\index{Grover's algorithm}
		\begin{itemize}
		\item Grover's algorithm \cite{bib:Grover96}.
		\item Quadratic speedup.
		\end{itemize}
	\item Satisfiability problems\footnote{A satisfiability problem is one where we search a function's input space for a solution(s) satisfying a given output constraint. The hardest such problems, like the archetypal \textsc{3-SAT}\index{3-\textsc{SAT}} problem, are \textbf{NP}-complete.}\index{\textbf{NP} \& \textbf{NP}-complete}:
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Includes solving \textbf{NP}-complete problems, and brute-force cracking of private encryption keys\footnote{Note that when performing a brute-force attack against a private encryption key\index{Private-key encryption}, a quadratic speedup effectively halves the key length in terms of algorithmic runtime. Thus, in the quantum era private key lengths will need to be doubled.}.\index{Satisfiability problems}
			\end{itemize}
	\item Optimisation problems:
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Many optimisation problems reside in \textbf{NP} or can be approximated in \textbf{NP}.\index{Optimisation problems}
			\end{itemize}
	\item Period finding and integer factorisation\index{Shor's algorithm}:
		\begin{itemize}
		\item Shor's algorithm \cite{bib:ShorFactor}.
		\item Exponential speedup.
		\item This compromises Rivest, Shamir \& Adleman (RSA) public-key cryptography \cite{bib:RSA}\index{RSA encryption}\index{Public-key encryption}, the most widely used cryptographic protocol on the internet today.
		\end{itemize}
	\item Simulation of quantum systems\index{Quantum simulation}:
		\begin{itemize}
			\item Lloyd's algorithm \cite{bib:lloyd1996universal}.
			\item Exponential speedup.
			\item This includes simulation of: molecular and atomic interactions in the study of quantum chemistry or nuclear physics; interactions between drug molecules and organic molecules for drug design; genetic interactions for the study of genetics and genetic medicine; nanoscale semiconductor physics for integrated circuit design; and much more.
			\end{itemize}
	\item Simulation of quantum field theories\index{Simulating quantum field theories}:
		\begin{itemize}
		 \item Jordan-Lee-Preskill algorithm \cite{bib:JLP, bib:RohdeWavelet15}
		 \item Exponential speedup.
		 \item A key area of fundamental physics research.
		 \end{itemize}
	\item Topological big-data analysis:\index{Topological big-data analysis}
		\begin{itemize}
		\item Lloyd's algorthm \cite{bib:lloyd2016quantum, USTCexperiment}.
		\item Exponential speedup.
		\item Broad applications including: social media network analysis; consumer behaviour; behavioural dynamics; neuroscience; and higher-dimensional signal and image processing.
		\end{itemize}
	\item Solving linear systems of equations:\index{Linear systems}
		\begin{itemize}
		\item \comment{To do} \cite{bib:harrow2009quantum, bib:BerryLinear}.
		\item Exponential speedup.
		\item Widespread applications in linear algebra and calculus.
		\end{itemize}
	\item Quantum machine learning:\index{Quantum machine learning}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2013quantum}.
		\item This includes putting an end to humanity.
		\item \textit{Ne obliviscaris}.
		\end{itemize}
\end{itemize}

\comment{Refere to algs section}

>>>>

\begin{itemize}
	\item Searching unstructured databases:\index{Grover's algorithm}
		\begin{itemize}
		\item Grover's algorithm \cite{bib:Grover96}.
		\item Quadratic speedup.
		\end{itemize}
	\item Satisfiability problems\footnote{A satisfiability problem is one where we search a function's input space for a solution(s) satisfying a given output constraint. The hardest such problems, like the archetypal \textsc{3-SAT}\index{3-\textsc{SAT}} problem, are \textbf{NP}-complete.}\index{\textbf{NP} \& \textbf{NP}-complete}:
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Includes solving \textbf{NP}-complete problems, and brute-force cracking of private encryption keys\footnote{Note that when performing a brute-force attack against a private encryption key\index{Private-key encryption}, a quadratic speedup effectively halves the key length in terms of algorithmic runtime. Thus, in the quantum era private key lengths will need to be doubled.}.\index{Satisfiability problems}
			\end{itemize}
	\item Optimisation problems:
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Many optimisation problems are \textbf{NP}-complete or can be approximated in \textbf{NP}-complete.\index{Optimisation problems}
			\end{itemize}
	\item Period finding and integer factorisation\index{Shor's algorithm}:
		\begin{itemize}
		\item Shor's algorithm \cite{bib:ShorFactor}.
		\item Exponential speedup.
		\item This compromises Rivest, Shamir \& Adleman (RSA) public-key cryptography \cite{bib:RSA}\index{RSA encryption}\index{Public-key encryption}, the most widely used cryptographic protocol on the internet today.
		\end{itemize}
	\item Simulation of quantum systems\index{Quantum simulation}:
		\begin{itemize}
			\item Lloyd's algorithm \cite{bib:lloyd1996universal}.
			\item Exponential speedup.
			\item This includes simulation of: molecular and atomic interactions in the study of quantum chemistry or nuclear physics; interactions between drug molecules and organic molecules for drug design; genetic interactions for the study of genetics and genetic medicine; nanoscale semiconductor physics for integrated circuit design; and much more.
			\end{itemize}
	\item Simulation of quantum field theories\index{Simulating quantum field theories}:
		\begin{itemize}
		 \item Jordan-Lee-Preskill algorithm \cite{bib:JLP, bib:RohdeWavelet15}
		 \item Exponential speedup.
		 \item A key area of fundamental physics research.
		 \end{itemize}
	\item Topological big-data analysis:\index{Topological big-data analysis}
		\begin{itemize}
		\item Lloyd's algorthm \cite{bib:lloyd2016quantum, USTCexperiment}.
		\item Exponential speedup.
		\item Broad applications including: social media network analysis; consumer behaviour; behavioural dynamics; neuroscience; and higher-dimensional signal and image processing.
		\end{itemize}
	\item Solving linear systems of equations:\index{Linear systems}
		\begin{itemize}
		\item \comment{To do} \cite{bib:harrow2009quantum, bib:BerryLinear}.
		\item Exponential speedup.
		\item Widespread applications in linear algebra and calculus.
		\end{itemize}
	\item Quantum machine learning:\index{Quantum machine learning}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2013quantum}.
		\item This includes putting an end to humanity.
		\item \textit{Ne obliviscaris}.
		\end{itemize}
\end{itemize}
An elementary technical overview of some of these archetypal algorithms is presented in Sec.~\ref{sec:quantum_algs}.
